Classification of Histopathological Images of Breast Cells between Malignant and Benign Tumors based on Handcrafted Feature Extraction

### 2019-11-22 docs/article.tex
Figures update

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}
\title{Classification of Histopathological Images of Breast Cells between Malignant and Benign Tumors based on Handcrafted Feature Extraction}
\author{Hiago Matheus Brajato \& André Furlan - UNESP - Universidade Estadual Paulista "Júlio de Mesquita Filho"}
\date{2019-11-14}
\maketitle

@@

\section{Classification}
The relevance of the descriptors, as well the performance of the classifiers were measured by the analysis of ROC Curve and area under curve ROC (AUC). This measures were used in the proposed method because the malignant an benign classes are unbalanced in dataset, being that there are 24 malignant samples and 26 benign ones. Taking this is consideration, it is not a good idea analysing the obtained results through measures as accuracy, because the calculation of this last measure does not take the class balancing into consideration.\par
The ROC Curve and AUC allow to analyse the performance of the classifiers through the confusion matrix obtained varying the threshold, so the plotted graph is formed by the X axis (1 - Specificity) and Y (Sensitivity), therefore, the AUC with value equals to 1 represents a perfect classification, while an AUC equals to 0.5 or less represents a random classification.\par
The performance of the proposed method was evaluated through the classifiers \textbf{Discriminant Analysis}, \textbf{Decision Tree} and \textbf{Naive Bayes}, taking into consideration that all of these classifiers were submitted to the K-Folds validation method, with K equals to 5.\par
The best number of descriptors found by testing the classifiers used in the present method can be seen in the Figure 10, which shows the number of descriptors used for the classification in X axis, and the average rates for AUC in the Y axis.\par
It is important to remember that the graph contained in the Figure 10 was obtained using the segmented images in the process; the best number of descriptors obtained (35) was also tested in the same process without the segmentation step, in order to determine the importance of this phase in the whole process. The AUC rates obtained for the Discriminant Analysis, Decision Tree and Naive Bayes were 0.83, 0.66 and 0.75 respectively, resulting in an average of 0.746, well below the value showed in the graph (0.823). This information show us that the segmentation step produces a significant improvement in the performance of the classifiers, being necessary use its during the proposed method.

@@

\section{Results}
lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum,

>>>>

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}
\title{Classification of Histopathological Images of Breast Cells between Malignant and Benign Tumors based on Handcrafted Feature Extraction}
\author{Hiago Matheus Brajato \& Andr√© Furlan - UNESP - Universidade Estadual Paulista "J√∫lio de Mesquita Filho"}
\date{2019-11-14}
\maketitle

@@

\section{Classification}
The relevance of the descriptors, as well the performance of the classifiers were measured by the analysis of ROC Curve and area under curve ROC (AUC). This measures were used in the proposed method because the malignant an benign classes are unbalanced in dataset, being that there are 24 malignant samples and 26 benign ones. Taking this is consideration, it is not a good idea analyzing the obtained results through measures as accuracy, because the calculation of this last measure does not take the class balancing into consideration.\par
The ROC Curve and AUC allow to analyse the performance of the classifiers through the confusion matrix obtained varying the threshold, so the plotted graph is formed by the X axis (1 - Specificity) and Y (Sensitivity), therefore, the AUC with value equals to 1 represents a perfect classification, while an AUC equals to 0.5 or less represents a random classification.\par
The performance of the proposed method was evaluated through the classifiers \textbf{Discriminant Analysis}, \textbf{Decision Tree} and \textbf{Naive Bayes}, taking into consideration that all of these classifiers were submitted to the K-Folds validation method, with K equals to 5.\par
The best number of descriptors found by testing the classifiers used in the present method can be seen in the Figure 10, which shows the number of descriptors used for the classification in X axis, and the average rates for AUC in the Y axis.\par
It is important to remember that the graph contained in the Figure 10 was obtained using the segmented images in the process; the best number of descriptors obtained (35) was also tested in the same process without the segmentation step, in order to determine the importance of this phase in the whole process. The AUC rates obtained for the Discriminant Analysis, Decision Tree and Naive Bayes were 0.83, 0.66 and 0.75 respectively, resulting in an average of 0.746, well below the value showed in the graph (0.823). This information show us that the segmentation step produces a significant improvement in the performance of the classifiers, being necessary use its during the proposed method.

@@

\section{Results}

discrim analysis
decision tree
naive bayes

Acur√°cia m√©dia de classifica√ß√£o: 0.763232
Acur√°cia m√©dia de classifica√ß√£o: 0.720606
Acur√°cia m√©dia de classifica√ß√£o: 0.676566

Acur·cia mÈdia de classificaÁ„o: 0.781414
Acur·cia mÈdia de classificaÁ„o: 0.654343
Acur·cia mÈdia de classificaÁ„o: 0.714747

lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum,
